---
title: "`mdcolor` Example"
output: html_notebook
---


```{r, echo=FALSE, results='asis'}
library(mdcolor)
mdcolor()
```

The `mdcolor` package allows you to [red]change text color [#] 
and [-orange] highlight text [#] in your document. `mdcolor` 
is fully compatible with *Markdown* syntax, but only is 
interpretable in HTML documents and slides. The main purpose 
of the package is further motivating students to use Rmarkdown 
and also, allow teachers/bloggers to produce more interesting 
documents by changing text color or highlighting text.

#### Where can it be applied?

`mdcolor` can change the text color anywhere in the document, 
including text paragraphs, headers, etc... 



#### [blue]Adding color to Rmarkdown[#]

`mdcolor` supports [-yellow]all R colors[#]. However, 
colors [-greenyellow][red]**MUST**[#][#] be specified 
by their name. If you don't know the R color names, type:

```{r, results='hide'}
colors()
```

More importantly, you need to include the results of the 
`mdcolor()` function `asis` inside the HTML document to 
append the required code for color interpretation. To do so, 
add the following code to your Rmarkdown document or slides:


<pre>
[red]
&#96;&#96;&#96;{r, echo=FALSE, results='asis'}  
library(mdcolor)
mdcolor()
&#96;&#96;&#96;
[#]
</pre>



General Syntax
==============

The general syntax for using `mdcolor` is as follows:

1. [red]Changing text color[#] = [`colorname`] text [`#`]
2. [blue]Highlighting text color[#] = [`-colorname`] text [`#`]

Note that for highlighting text, the color name _begins with a 
minus_!

The `[hash]` sign is a preserved closing marker that ends 
the previous `mdcolor` code. You can find out more about 
`mdcolor` or further colaborate on the code in the GitHub 
repository https://github.com/haghish/mdcolor


Using `mdcolor` on the web
==========================

`mdcolor` is not limited to **R** and can be used on any website
or HTML document to highlight text using the specified 
syntax. To do so, you can simply source the [JavaScript file in your document!](https://raw.githubusercontent.com/haghish/mdcolor/master/inst/mdcolor.js) 


[red]

~~~
[red]<script src=[#][darkgreen]"https://raw.githubusercontent.com/haghish/mdcolor/master/inst/mdcolor.js"[#][red]></script>[#]
~~~

-----------

**All these colors were added using `mdcolor` and `Rmarkdown`!**

