---
title: "mdcolor package Test"
author: "E. F. Haghish"
date: "1/8/2018"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE )
```

```{r, echo=FALSE, results='asis'}
library(mdcolor)
mdcolor()
```

### [orange]`mdcolor` Package[#]

[red]`mdcolor`[#] package allows you to change text color inside HTML and Markdown documents and also highlight the text in a variety of colors. to do so, you should add the JavaScript file to your document. the code **MUST** be added with an additional argument of **`results='asis'`** in R Markdown:


```{r}
library(mdcolor)
```

Now let's add the `mdcolor.js` to our document. remember that 
you have to add the `results='asis'` code in the chunk's header

```{r, results='asis'}
#REMEMBER:   results = 'asis'
mdcolor()
```




[green]Fun Begins![#]
===================

This is an R [-yellow] Markdown document[#] . [-purple]Markdown[#] is a simple formatting syntax for authoring [green]HTML[#], [blue]PDF[#], and [red]MS[#] Word documents. 
As you can see, the `mdcolor` package can bring colors to Markdown documents, allowing to change text color or highlight it... 

**GitHub Repository**:  https://github.com/haghish/mdcolor

All [-hotpink]R[#] [orangered]colors[#] 
are [-greenyellow][orange]**AVAILABL**[#][#]

